Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-15 bbbq_article.tex
Use violin plot, fix #94

Evolutionary conservation scores are shown in 
figures \ref{fig:evolutionary_conservation} (topology)
and \ref{fig:evolutionary_conservation_boxplot} (boxplot)
for proteins that have at least one TMH (see figures
\ref{fig:evolutionary_conservation_all} and 
\ref{fig:evolutionary_conservation_all_boxplot}
for the scores for all proteins).

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation_boxplot}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_boxplot_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins
  }
  \label{fig:evolutionary_conservation_all_boxplot}
\end{figure}

>>>>

Evolutionary conservation scores are shown in 
figures \ref{fig:evolutionary_conservation} (topology)
and \ref{fig:evolutionary_conservation_violin} (boxplot)
for proteins that have at least one TMH (see figures
\ref{fig:evolutionary_conservation_all} and 
\ref{fig:evolutionary_conservation_all_violin}
for the scores for all proteins).

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for proteins that have at least one TMH
  }
  \label{fig:evolutionary_conservation_violin}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/scores_violin_all.png}
  \caption{
    Evolutionary conservation scores of TMH versus non-TMH
    residues in the SARS-CoV-2 proteome,
    for all proteins
  }
  \label{fig:evolutionary_conservation_all_violin}
\end{figure}
